---
title: "Class3_09_15_2026"
author: Andrea
date: "2026-09-15"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

# Section 1

Here is a **code chunk** that samples from 
a _normal distribution_:

```{r}
 samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Section 3

### Data Frame and plots

The code chunk below creates a data frame and generates a plot.

```{r plot_example}
library(tidyverse)

plot_df = tibble(
  x = rnorm(500, mean = 2, sd = 4),
  y = 3 - 4.2 * x + rnorm(500)
)


ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This plot is really great!! It shows a linear relationship just as expected. 

# Section 4: In line code:

We can use in line code to provide data in our text, such as:

The data frama has `r nrow(plot_df)` rows.

Know that the code that was ran in line was `` r``

# Section 4: Text formatting:

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings: 
------------------------------------------------------------
The symbol # marks a section heading and within a code chunk a comment.

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

> this is a clock quote.


# learning Check 2: 

Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r Learning_assesment_1}

la_df = tibble (
  norm_samp = rnorm(500, mean = 1),
  norm_samp_pos = norm_samp > 0, 
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x =abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
``` 
the median of the variable containing absolute value is `r round(median_samp, digits = 2)`.


